Statistical Stopping Criteria for Active Learning in Systematic Review Screening

### 2019-07-23 manuscript/main.tex
add paragraph on information retrieval stopping criteria literature

>>>>

	The information retrieval literature discusses similar stopping criteria for ranking algorithms like BM25 and variants \cite{DiNunzio2018, Yu2019}. However, the estimators they use to determine the recall rely on the specific ranking functions and depend on their search input. Therefore, the quality of the estimation depends on the adequacy of the model. Our approach, on the contrary, is model-free.
